---
title: "Homework7"
author: "Andre LaFleur"
date: "December 1, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Problem 1

Below is the Fisher test of the data provided:

```{r}
cardiac = read.csv("cardiac.dat")

# First let's gather up all the data into a contingency matrix
malesWith = 0
malesWithout = 0
femalesWith = 0
femalesWithout = 0

# Kinda hacky, but whatever
for(i in 1:nrow(cardiac)){
  if(cardiac[i, "gender"] == 0){
    if(cardiac[i,"hxofHT"] == 0) { 
      malesWith = malesWith + 1
    } else { 
        malesWithout = malesWithout + 1
    }
  } else {
    if(cardiac[i,"hxofHT"] == 0){
      femalesWith = femalesWith + 1
    } else {
      femalesWithout = femalesWithout + 1
    }
  }
}

# Now the contingency matrix and fisher test
C = matrix(c(malesWith, malesWithout, femalesWith, femalesWithout), 2, 2)
fisher.test(C, alternative = "greater")

```

According to the Fisher test, $p = 0.9848$. I don't think the null hypothesis can be rejected at $\alpha=0.05$, since
the confidence interval is still very close to $0.5$.

# Problem 2

```{r}
maleBP = cardiac$basebp[cardiac$gender == 0]
femaleBP = cardiac$basebp[cardiac$gender == 1]
```

## PART A

The alternate hypothesis is the one we are interested in - that is, "women have a lower resting blood pressure than men." The null hypothesis
would be the opposite - "women have a higher resting blood pressure than men."

## PART B

```{r}
boxplot(maleBP, femaleBP, names = c("Male Resting Blood Pressure", "Female Resting Blood Pressure"))
```

## PART C


## PART D

## PART E

# Problem 3

## PART A

The alternative hypothesis would be that there is some correlation between petal length
and sepal length - that is, $\rho(x, y) \neq 0$.

## PART B

```{r}
x = iris$Petal.Length
y = iris$Sepal.Length
plot(x, y, main="Petal and Sepal Lengths", xlab="Petal Length", ylab="Sepal Length")
```

## PART C

TODO: This
```{r}
```

## PART D

```{r}
t = cor(x, y) * sqrt(148/(1-cor(x, y)^2))
print(t)
```

## PART E

## PART F

The alternative hypothesis would be that there is some correlation between sepal width
and sepal length.

## PART G

```{r}
x = iris$Sepal.Width
y = iris$Sepal.Length
plot(x, y, main="Sepal Widths and Lengths", xlab="Sepal Width", ylab="Sepal Length")
print(paste("T: ", cor(x, y) * sqrt(148/(1-cor(x, y)^2))))
```

# Problem 4

```{r}
## Calculates regression given x and y vectors. Returns c(slope, intercept)
myregression = function(x, y){
  sum_of_products = 0
  sum_of_squares = 0
  
  for(i in 1:length(y)){
    sum_of_products = sum_of_products + x[i] * y[i]
    sum_of_squares = sum_of_squares + x[i]^2
  }
  
  n_products = sum_of_products * length(x)
  
  beta = (n_products - (sum(x) * sum(y)))/(length(x) * sum_of_squares - sum(x)^2)
  
  return(c(beta, mean(y)))
}
```


## PART A

```{r}
x=faithful$waiting
y=faithful$eruptions

regression = myregression(x, y)
cat(paste("Slope\t", regression[1]))
cat(paste("Intercept\t", regression[2]))
plot(x, y, main="Old Faithful Eruptions and Waiting Times", xlab="Waiting Period", ylab="Eruption Period")
abline(a=regression[1], b=regression[2], col="red")
```

## PART B

```{r}

```

## PART C

```{r}
print(lm(y ~ x))
print(regression)
```

## PART D


