---
title: "Homework7"
author: "Andre LaFleur"
date: "December 1, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Problem 1

Below is the Fisher test of the data provided:

```{r}
cardiac = read.csv("cardiac.dat")

# First let's gather up all the data into a contingency matrix
malesWith = 0
malesWithout = 0
femalesWith = 0
femalesWithout = 0

# Kinda hacky, but whatever
for(i in 1:nrow(cardiac)){
  if(cardiac[i, "gender"] == 0){
    if(cardiac[i,"hxofHT"] == 0) { 
      malesWith = malesWith + 1
    } else { 
        malesWithout = malesWithout + 1
    }
  } else {
    if(cardiac[i,"hxofHT"] == 0){
      femalesWith = femalesWith + 1
    } else {
      femalesWithout = femalesWithout + 1
    }
  }
}

# Now the contingency matrix and fisher test
C = matrix(c(malesWith, malesWithout, femalesWith, femalesWithout), 2, 2)
fisher.test(C, alternative = "greater")

```

According to the Fisher test, $p = 0.9848$. I don't think the null hypothesis can be rejected at $\alpha=0.05$, since
the confidence interval is still very close to $0.5$.

# Problem 2

```{r}
maleBP = cardiac$basebp[cardiac$gender == 0]
femaleBP = cardiac$basebp[cardiac$gender == 1]
```

## PART A

The alternate hypothesis is the one we are interested in - that is, "women have a lower resting blood pressure than men." The null hypothesis
would be the opposite - "women have a higher resting blood pressure than men."

## PART B

```{r}
boxplot(maleBP, femaleBP, names = c("Male Resting Blood Pressure", "Female Resting Blood Pressure"))
```

## PART C


## PART D

# Problem 3
# Problem 4