---
title: "Homework3"
author: "Andre LaFleur"
date: "October 3, 2016"
output: html_document
---

# Problem 1

The distribution of M would be a geometric distribution. Assuming that the probabilities of winning either
one of the lotteries is the same each round, then with each subsequent attempt at winning either the
probability of winning one goes up. Its parameter would be $p~1~ + p~2~$, as the geometric distribution
must take into account the probabilities of both lotteries.

# Problem 2

Let F be the event "the software recognized the face correctly". It is that the software is used 50 times
a day and $P(F) = 0.9$. The distribution function associated with this scenario must be a Binomial
distribution, as there are only two results from each use of the face recognition software: that the face
was recognized or it was not. Thus let $\Theta = P(F) = 0.9$. The probability formula will be
$P(F = k) = {50 \choose k} P(F)^k * P(F)^{50-k}$, for some $k$ faces correctly recognized.

## Part A

According to the formula given previously, it is expected that $P(F^c = 8) = P(F = 42) = 0.06427787788$ Below is the
function in R:

```{r}
dbinom(42, size = 50, prob = 9/10)
```

## Part B

According to the formula given above, for $P(F^c <= 5) = P(F >= 45) = P(F = 45) + P(F = 46) + ... + P(F = 50) = 0.616$. Thus we need
to sum five differenet binomial distribution evaluations together, as shown below:

```{r}
dbinom(45, size = 50, prob = 9/10) + dbinom(46, size = 50, prob = 9/10) + dbinom(47, size = 50, prob = 9/10) + dbinom(48, size = 50, prob = 9/10) + dbinom(49, size = 50, prob = 9/10) + dbinom(50, size = 50, prob = 9/10)
```

## Part C

According to the formula given above, $P(F = 50) = 0.0051537752$. Below is the solution in R:

```{r}
dbinom(50, size = 50, prob = 9/10)
```

# Problem 3

```{r}
days = 10000 # The number of days we're trying out

# Function that returns the number of faces recognized in a given day
simulateDay = function(){
  facesPerDay = 50
  facesRecognized = 0
  
  for(i in 1:facesPerDay){
    
    if(runif(1, 0, 1.0) < 0.9){
      facesRecognized = facesRecognized + 1
    }
  }
  
  return(facesRecognized);
}

### PART A ###

experiment = replicate(days, simulateDay())
res = experiment[experiment == 42]
cat(paste("PART A: ", length(res) / days))

### PART B ###

experiment = replicate(days, simulateDay())
res = experiment[experiment >= 45]
cat(paste("PART B: ", length(res) / days))

### PART C ###

experiment = replicate(days, simulateDay())
res = experiment[experiment == 50]
cat(paste("PART B: ", length(res) / days))
```

# Problem 4

# Problem 5

# Problem 6
