---
title: "Homework3"
author: "Andre LaFleur"
date: "October 3, 2016"
output: html_document
---

# Problem 1

The distribution of M would be a geometric distribution. Assuming that the probabilities of winning either
one of the lotteries is the same each round, then with each subsequent attempt at winning either the
probability of winning one goes up. Its parameter would be $p~1~ + p~2~$, as the geometric distribution
must take into account the probabilities of both lotteries.

# Problem 2

Let F be the event "the software recognized the face correctly". It is that the software is used 50 times
a day and $P(F) = 0.9$. The distribution function associated with this scenario must be a Binomial
distribution, as there are only two results from each use of the face recognition software: that the face
was recognized or it was not. Thus let $\Theta = P(F) = 0.9$. The probability formula will be
$P(F = k) = {50 \choose k} P(F)^k * P(F)^{50-k}$, for some $k$ faces correctly recognized.

## Part A

According to the formula given previously, it is expected that $P(F^c = 8) = P(F = 42) = 0.06427787788$ Below is the
function in R:

```{r}
dbinom(42, size = 50, prob = 9/10)
```

## Part B

According to the formula given above, for $P(F^c <= 5) = P(F >= 45) = P(F = 45) + P(F = 46) + ... + P(F = 50) = 0.616$. Thus we need
to sum five differenet binomial distribution evaluations together, as shown below:

```{r}
dbinom(45, size = 50, prob = 9/10) + dbinom(46, size = 50, prob = 9/10) + dbinom(47, size = 50, prob = 9/10) + dbinom(48, size = 50, prob = 9/10) + dbinom(49, size = 50, prob = 9/10) + dbinom(50, size = 50, prob = 9/10)
```

## Part C

According to the formula given above, $P(F = 50) = 0.0051537752$. Below is the solution in R:

```{r}
dbinom(50, size = 50, prob = 9/10)
```

# Problem 3

```{r}
days = 10000 # The number of days we're trying out

# Function that returns the number of faces recognized in a given day
simulateDay = function(){
  facesPerDay = 50
  facesRecognized = 0
  
  for(i in 1:facesPerDay){
    
    if(runif(1, 0, 1.0) <= 0.9){
      facesRecognized = facesRecognized + 1
    }
  }
  
  return(facesRecognized);
}

### PART A ###

experiment = replicate(days, simulateDay())
res = experiment[experiment == 42]
cat(paste("PART A: ", length(res) / days))

### PART B ###

experiment = replicate(days, simulateDay())
res = experiment[experiment >= 45]
cat(paste("PART B: ", length(res) / days))

### PART C ###

experiment = replicate(days, simulateDay())
res = experiment[experiment == 50]
cat(paste("PART B: ", length(res) / days))
```

# Problem 4

Let $X ~ Geom(\Theta)$, where $\Theta$ is the probability of the couple having a girl. 
Given that the probability of having a girl $\Theta = 0.5$, the probability mass function for this scenario would be 

$$P(X=k) = (1-\Theta)^{k - 1} * \Theta = 0.5^{k-1} * 0.5 = 0.5^{k}$$

as this scenario matches that of a geometric distribution.

## Part A

The probability of having more boys than girls is $P(X \geq 3)$, as the couple must have at least 3 children to have more
boys than girls. That probability is solved here: 

$$\begin{align}
P(X \geq 3) &= 1 - P(X \leq 2)\\
&= 1 - (P(X = 1) + P(X = 2))\\
&= 1 - (0.75) \\
&= 0.25
\end{align}
$$

Given this information, it is most likely that they will either have just one girl, or one boy and one girl. This makes
it most probable that the couple will have more girls than boys (due to having no boys), or have an equal number of the two.

## Part B

Using the formula above, the probability that the couple has exactly $k$ boys would be that of our original formula, plus
one; that is, $P(X=k) = 0.5^{k + 1}$, where $k$ is the number of boys. This is because the original formula assumed that
the kth child of the couple is a girl, but what we desire is the formula that gives us the probability for $k$ boys. Thus
we can modify our original formula by simply adding one, because if a couple ends up having $k$ boys given the parameters
spelled out before, then the $k+1$th child must be a girl.

## Part C

Given that the probability of having a boy is 0.6, then $\Theta = 0.4$. This changes our formula to

$$P(X=k) = 0.6^{k - 1} * 0.4$$

where $k$ is the number of children the couple would have. Given this is the case, consult the following
values for $P(X=k)$:

|  $k$  |  $P(X=k)$  |
|:-----:|:----------:|
|  $1$  |   $0.4$    |
|  $2$  |   $0.24$   |
|  $3$  |   $0.144$  |
|  $4$  |  $0.0864$  |

Therefore, for the couple to have more boys than girls, that would mean the couple must have at least three children
for this to be the case. We can solve for that probability:

$$\begin{align}
P(X \geq 3) &= 1 - P(X \leq 2)\\
&= 1 - (P(X = 1) + P(X = 2))\\
&= 1 - (0.64)\\
&= 0.36
\end{align}
$$

This implies that it is more likely that the couple will have one boy and one girl, or just one girl, in spite of the
fact that $\Theta = 0.4$.

## Part D

The probability of having exactly $k$ boys is simply the probability of the $k+1$th child being a girl, making our formula
simply

$$P(X=k) = 0.6^{k} * 0.4$$

# Problem 5

We are given a piecewise function as the probability density function for our continuous random variable:

$$
f(x) = \left\{
     \begin{array}{lr}
       4x & : 0 \leq x \leq \frac{1}{2}\\
       4 - 4x & : \frac{1}{2} \leq x \leq 1 \\
       0  & : x \leq 0 \cup x \geq 1
     \end{array}
     \right.
$$

## Part A

To see what the probability of a student failing the exam is, given that the point of failure is $0.55$, we are confronted with
the following integral:

$$\int_0^0.55 f(x) dx$$

Since $f(X)$ is a peicewise function, that interval is relatively trivial to solve:

$$\begin{align}
\int_0^0.55 f(x) dx &= \int_0^0.5 4x dx + \int_0.5^0.55 4 - 4x dx\\
&= 2x^2 \big|_0^{0.5} + 4x - 2x^x \big|_{0.5}^{0.55}\\
&= 0.595
\end{align}
$$

Thus the probability that a student will fail the exam is $0.595$.

## Part B

To figure out what the 50th percentile of this distribution is, we must solve $P(X \leq q) = p$, where $p$ is the percentile
we are trying to solve - in this case, $p = 0.5$. Thus we use our function to solve for q like so:

$$\begin{align}

\end{align}
$$

# Problem 6

















