---
title: "homework2.rmd"
author: "Andre LaFleur"
date: "September 20, 2016"
output: html_document
---

# Problem 1

Let $W$ be the event of a white ball being drawn, and $R$ be the event of a red ball being drawn.
In this problem we are asked to calculate $P(R_{2} \cap R_{1})$, given that whenever a red ball is drawn
the ball is returned to the urn. Thus the probability of drawing a red ball on the first draw, or $P(R_1)$,
is $P(R_1) = \frac{1}{2}$, while $P(R_2) = \frac{3}{4}$, etc. Given this information, this calculation is 
relatively straightforward:

$$
\begin{align}
P(R_2 \cap R_1) &= P(R_2 | R_1) * P(R_1) & \text{Multiplication rule}\\
&= \frac{3}{4} * \frac{1}{2}&  \\
&= \frac{3}{8} &\\
\end{align}
$$

# Problem 2

```{r}
# The urns 
first = c("R", "W") # "Given W1" is identical to first
givenR1 = c("R", "R", "R", "W")
omega = c("RR", "RW", "WR", "WW")

trials = 10000
twoRs = 0

for(i in 1:trials) {
  draw1 = sample(first, 1, TRUE)
  draw2 = sample(givenR1, 1, TRUE)
  
  if(("R" %in% union(draw1, draw2)) & !("W" %in% union(draw1, draw2))){
    twoRs = twoRs + 1
  }
}

cat(paste("P(R2) = ", twoRs / trials, "\t Expected: ", 3 / 8))

```

# Problem 3

a) Below is the probability tree for the two events. Let event H = "A hurricane causes a landfall" and
event P = "The meteoroligist properly predicted H":

| $H$   | $P$   | $0.9$ |
|-------|-------|-------|
|       | $P^c$ | $0.1$ |
| $H^c$ | $P$   | $0.15$|
|       | $P^c$ | $0.85$|

Below are the values of intersection:

$$\begin{align}
H \cap P &= 0.63\\
H \cap P^c &= 0.07\\
H^c \cap P &= 0.045\\
H^c \cap P^c &= 0.255\\
\end{align}
$$

b) The total probability of event P can be solved as follows:

$$\begin{align}
P(P) &= P(P \cap H) + P(P \cap H^c) & \text{Definition of total probability}\\
&= 0.63 + 0.045\\
&= 0.675
\end{align}
$$

c) If a meteoroligist predicts that a hurricane will hit land, then the probability that
it actually will, or $P(H|P)$ can be solved as follows:

$$\begin{align}
P(H|P) &= \frac{P(P|H)P(P)}{P(H)} &= \text{Bayes' Rule}\\
&= \frac{0.9 * 0.675}{0.7}\\
&= 0.86\\
\end{align}
$$

# Problem 4

a) Given that A is the event "the result of a roll of 1d6 is less than or equal to 4" and B is the
event "the result of the roll of a 1d6 is odd", then for events A and B to be independent,
$P(A|B) = P(A)$. The only results from event A can be the set $\{1, 2, 3, 4\}$ and the result set of
event B must be $\{1, 3, 5\}$. The probabilities, however, are as follows:

$$\begin{align}
P(A) &= \frac{|A|}{|\Omega|} & \text{Definition of probability given sets}\\ 
&= \frac{4}{6}\\ 
&= \frac{1}{3}\\
\\
P(A|B) &= \frac{|A \cap B|}{|B|} & \text{Definition of conditional probability} \\
&= \frac{2}{4}\\ 
&= \frac{1}{2}\\
\end{align}
$$

Since $P(A|B) \neq P(A)$, the two events must be dependent.

b) For A and B to be independent, $P(A|B) = P(A)$. Below is the calculation of the two separate
probabilities:

$$\begin{align}
P(A) &= \frac{|\{HH, TT\}|}{|\Omega|} & \text{Definition of probability given sets}\\
&= \frac{2}{4}\\
&= \frac{1}{2}\\
\\
P(A|B) &= \frac{P(A \cap B)}{P(B)} & \text{Definition of conditional probability}\\
&= \frac{\frac{1}{2} * \frac{1}{2}}{\frac{1}{2}}\\
&= \frac{1}{2}
\end{align}
$$

Since $P(A|B) = P(A)$, the two events must be independent.

# Problem 5

This problem gives a few peices of information, with which part of a conditional probability tree can be built.
Below is this tree, where A is the event "the patient has the disease" and B is the event "the test
returned a positive result":

| $A$   | $B$   | $0.85$ |
|-------|-------|--------|
|       | $B^c$ |   -    |
| $A^c$ | $B$   | $0.1$  |
|       | $B^c$ |    -   |

The problem also mentions that $P(A) = 0.3$ Given this information, the requested probability,
$P(A|B)$, can be solved using Bayes' rule, and the total probability $P(B)$:

$$\begin{align}
P(A|B) &= \frac{P(B|A)P(A)}{P(B)} &\text{Bayes' Rule}\\
&= \frac{P(B|A)P(A)}{P(A \cap B) + P(A \cap B^c)} &\text{Definition of total probability}\\
&= \frac{0.85 * 0.3}{0.325}\\
&= 0.2615
\end{align}
$$

# Extra Credit

```{r}
genders = c("M", "F")
daysOfWeek = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday")
trials = 1000000

genderSample = sample(genders, trials, TRUE)
daysSample = sample(daysOfWeek, trials, TRUE)

boys = 0 # Event A = "Boy is born"
boysOnTuesday = 0 # Event B = "Boy is born on Tuesday"

for(i in 1:trials){
  gender = genderSample[i]
  day = daysSample[i]
  
  if("M" %in% gender){
    boys = boys + 1
    
    if("Tuesday" %in% day){
      boysOnTuesday = boysOnTuesday + 1
    }
  }
}

cat(paste("Let A = \"boy born\" and B = \"boy born on Tuesday\".\n\n", "P(A) = ", boys / trials, "\n", "P(A|B) = |A & B| / |B| = ", boysOnTuesday / boys))

```

