---
title: "Homework 4"
author: "Andre LaFleur"
date: "October 18, 2016"
output: html_document
---

# Problem 1

## Part A

For $f(x)$ to be a valid probability density function, $\int_{-\infty}^{\infty} f(x) dx = 1$. Since the integral for
all values outside of the boundary $0 \leq x \leq c$ is simply zero, we can solve for c using the following integral:

$$\begin{align}
\int_{0}^{c} 4x + 1 dx &= 1 \\
2x^2 + x \big|_{0}^{c} &= 1 \\
2c^2 + c &= 1 \\
2c^2 + c - 1 &= 0 \\
c = \frac{1}{2} \text{or} -1 &\text{By the quadratic equation} \\
\end{align}
$$

Since the boundary $0 \leq x \leq -1$ doesn't make much sense, $c = \frac{1}{2}$

## Part B

The expected value of X, $E[X]$, is given by the following equation: $$E[X] = \int_0^{\frac{1}{2}} x f(x) dx$$

The value then of $E[X]$ is the following:

$$\begin{align}
\int_{0}^{\frac{1}{2}} 4x^2 + x dx &= \frac{4x^3}{3} + \frac{x^2}{2} \big|_0^{\frac{1}{2}}\\
&= \frac{\frac{1}{2}}{3} + \frac{1}{8}\\
&= \frac{7}{24}
\end{align}
$$

## Part C

The variance of X, or $Var(X)$, can be solved given the formula $Var(X) = E[X^2] - E[X]^2$. Thus we can solve
for the value of the variance:

$$\begin{align}
E[X^2] - E[X]^2\\
\int_0^{\frac{1}{2}} x^2 f(x) dx - (\frac{7}{24})^2\\
\int_0^{\frac{1}{2}} 4x^3 + x^2 dx - (\frac{7}{24})^2\\
x^4 + \frac{x^3}{3} \big|_0^{\frac{1}{2}} - (\frac{7}{24})^2\\
\frac{1}{16} + \frac{1}{24} - (\frac{7}{24})^2\\
\approx 0.0190972
\end{align}
$$

## Part D

Let $g(x) = 2X + 3 = 2f(x) + 3 = 8x + 5$. Since $E[2X + 3] = E[g(x)]$, we can solve for this expected value
as follows:

$$\begin{align}
\int_{0}^{\frac{1}{2}}g(x)f(x)dx\\
\int_{0}^{\frac{1}{2}}(8x+5)(4x+1)dx\\
\int_{0}^{\frac{1}{2}}32x^2+28x+5dx\\
\frac{32x^3}{3}+14x^2+5x \big|_0^{\frac{1}{2}}\\
\frac{4}{3} + \frac{7}{2} + \frac{5}{2}\\
\frac{22}{3}
\end{align}
$$

## Part E

Since we have solved for $E[g(X)]$, we can use the previous formula for variance to solve for $Var(g(X))$:

$$\begin{align}
E[g(x)^2] - E[g(x)]^2 \\
&= \int_{0}^{\frac{1}{2}}g(x)^2 * f(x) dx - (\frac{22}{3})^2 \\
&= \int_{0}^{\frac{1}{2}}(64x^2+80x+25)(4x + 1) dx - (\frac{22}{3})^2 \\
&= \int_{0}^{\frac{1}{2}}256x^3+384x^2+180x+25 dx - (\frac{22}{3})^2 \\
&= 64x^4+128x^3+90x^2+25x\big|_0^{\frac{1}{2}}  - (\frac{22}{3})^2 \\
&= 55 - (\frac{22}{3})^2\\
&\approx 1.22222222222
\end{align}
$$

# Problem 2

Let $X ~ Geom(\Theta)$, where $\Theta = 0.5$, the probability of getting a heads after flipping a fair coin. This implies then
that $E[X] = \frac{1}{\Theta} = 2$. Since we are searching for the expected number of coin flips to get three heads, we are actually
looking for $E[3X] = 3E[X] = (3)(2) = 6$. Therefore, if we flip a fair coin until we get three heads, the expected number of flips would
be $6$.

# Problem 3

Since $X ~ Unif(-\pi, 0)$, $E[\sin{X}]$ is relatively straightforward integral to solve:

$$\begin{align}
E[\sin{X}] &= \int_{-\pi}^{0}\frac{\sin{x}}{\pi} dx \\
&= \frac{-\cos{x}}{\pi}\big|_{-\pi}^0 \\
&= \frac{-\cos{0}}{\pi} + \frac{\cos{-\pi}}{\pi} \\
&= -\frac{2}{\pi} \\
&\approx -0.636619 \\
\end{align}
$$

# Problem 4

```{r}
trials = 100000
numbers = sin(runif(trials, min = -pi, max = 0))

cat(paste("Mean: ", mean(numbers), "\n-2/pi: ", -2 / pi))
```


# Problem 5

Let $X: [1, 6] \rightarrow [0, 2]$, wherein the random variable $X$ maps the set $\{1, 2\}$ onto 
$0$, $\{3, 4, 5\}$ onto $1$, and $\{6\}$ onto $2$. The random variable $X$ now represents the game
with jellybeans described.

## Part A

The expected number of jellybeans, or the expected value of X, $E[X]$, is given below:

$$\begin{align}
E[X] &= \sum_{i=0}^{2}a_iP(X = a_i) & \text{Definition of E[X] for a discrete random variable}\\
&= 0(\frac{1}{3}) + 1(\frac{1}{2}) + 2(\frac{1}{6})\\
&= \frac{5}{6}
\end{align}
$$

## Part B

The variance of $X$, $Var(X)$, is found as follows:

$$\begin{align}
E[(X-E[X])^2] &= \sum_{i=0}^{2}P(X = i)(i - \frac{5}{6})^2 & \text{Definition of Var(X) for a discrete random variable}\\
&= \frac{1}{3}(- \frac{5}{6})^2 + \frac{1}{2}(\frac{1}{6})^2 + \frac{1}{6}(\frac{7}{6})^2\\
&= \frac{1}{3}\frac{25}{36} + \frac{1}{2}\frac{1}{36} + \frac{1}{6}\frac{49}{36}\\
&= \frac{25}{108} + \frac{1}{72} + \frac{49}{216}\\
&\approx0.4722222
\end{align}
$$

## Part C

This is not a game you would like to play if you like jelly beans. Since the expected number of jelly beans that you
would get per round ends up being $\frac{5}{6}$, and it costs a jelly bean each time you play, you would expect
to lose $1 - \frac{5}{6} = \frac{1}{6}$ jellybeans per round. 

# Problem 6
```{r}
trials = 40000
jellybeans = c()

for(i in 1:trials){
  dieRoll = sample(c(1, 2, 3, 4, 5, 6), 1, replace = TRUE)
  
  if(dieRoll <= 2){
    jellybeans[i] = 0
  } else if(dieRoll <= 5){
    jellybeans[i] = 1
  } else {
    jellybeans[i] = 2
  }
}

cat(paste("Expected value of jellybeans: ", mean(jellybeans), "\n5/6: ", 5 / 6))
```

# Extra Credit

The table below compares the number of points one would score on the exam, given the two 
grading schemes my professor has provided:

| Correct Answers |   0    |   1    |    2   |    3   |   4    |   5    |    6   |    7   |    8   |   9    |   10   |
|:---------------:|:------:|:------:|:------:|:------:|:------:|:------:|:------:|:------:|:------:|:------:|:------:|
| Scheme 1        |   0    |   10   |   20   |    30  |   40   |   50   |    60  |   70   |   80   |   90   |   100  |
| Scheme 2        | -100   |  -75   |  -50   |  -25   |   0    |   25   |   50   |   75   |   100  |  125   |  150   |

According to the table above, grading scheme two pays off if I were to get at least 7 questions correct, as it gives me
more points than grading scheme one would. If I desire getting a passing grade (70 points or higher), I would want to
get at least 7 questions correct. Let $X_1 ~ Binom(10, p)$ representing the first grading scheme, and $X_2 ~ Binom(10, p)$
representing the second grading scheme. Since we hope to get at least 7 questions correct, we will solve for $p$ in $E[X]$:

$$\begin{align}
E[X_1] &= 10p & E[X_2] &= 10p \\
7 &= 10p & 7 &= 10p \\
p = \frac{7}{10} && p = \frac{7}{10} \\
\end{align}
$$

If I typically score a passing grade on everything else I do, that is, if $p = \frac{7}{10}$, then either grading scheme
will provide me a passing grade, although grading scheme two will offer me more points than grading scheme one. So if I'm
an average student and I would like an average grade, $p = \frac{7}{10}$ and either scheme would give me the grade I seek,
I would pick scheme two, as I will get more points than if I pick scheme one. If $p < \frac{7}{10}$, scheme one would be the
best option, as I will score more points than scheme two. If $p > \frac{7}{10}$, scheme two would definitely be the best
option, as if I simply miss two questions I will get over 100 points.