---
title: "Homework6"
author: "Andre LaFleur"
date: "November 17, 2016"
output: html_document
---

# Problem 1

## Part A

Let $X ~ Bin(n, \frac{1}{2})$, where $n$ is the number of coin flips my friend will make. What my friend
ends up providing is some number, $x_i$, representing the number of those coins that were heads.

We can come up with an unbiased statistic, or $\hat{n}$, using the following equation:

$$\begin{align}
E[X_i] &= E[\overline{X}_10] \\
&= \frac{1}{10}E[\Sigma_{i = 1}^{10} X_i] \\
&= E[X_i] \\
&= n/2 \\
\Rightarrow \hat{n} &= 2E[X_i] \\
\end{align}
$$

## Part B

```{r}
n = 25
probability = 1/2
trials = 10000
n_hats = c()

## Each experiment
for(i in 1:trials){
  heads = 0
  
  # Tossing 25 coins
  for(j in 1:n){
    if(runif(1) > probability){
      heads = heads + 1
    }
  }
  
  n_hats[i] = 2 * heads # n_hat = 2 * E[X_i]
}

cat(paste("n hat: ", mean(n_hats), "; expected ", n))
```

## Part C

```{r}
boxplot(0:50,data=n_hats, main = "Expected value of X")
abline(h = n, col = "red")
```

## Part D

```{r}
hist(n_hats, freq = FALSE)
s = seq(-25, 25, 0.05)
lines(s, dnorm(s), col = 'red', lwd = 2)
```

# Problem 2

The confidence interval is given by the formula $X_n \pm z_{\frac{\alpha}{2}}(\frac{\sigma}{\sqrt{n}})$. We are given
values in the problem, that is $n = 10$, $\overline{X}_10 = 94 kg$, $\overline{x} = 93.5 kg$, and $\sigma = 0.75$.
Given that $z_{\frac{\alpha}{2}} = P(1 - \alpha)$, and we are to use $\alpha = 0.05$, the solution is a matter of
"plugging and chugging":

```{r}
n = 10
alpha = 0.05
mean_x = 93.5
sigma = 0.75
z_alpha_over_two = qnorm(1 - 0.5 * alpha)

lower_bound = mean_x - z_alpha_over_two * (sigma / sqrt(n))
upper_bound = mean_x + z_alpha_over_two * (sigma / sqrt(n))

cat(paste("Lower bound:\t", lower_bound, "\nUpper bound:\t", upper_bound))
```

# Problem 3

## Part A

Given that our confidence interval was $(1.6, 7.8)$, then the mean would simply be the value directly between
them, as shown below:

$$\begin{align}
\overline{X_n} - z_{\frac{\alpha}{2}} * (\frac{\sigma}{srt(n)}) &\leq \mu &\leq \overline{X} + z_{\frac{\alpha}{2}} * (\frac{\sigma}{srt(n)}) \\
\overline{X_n} &\leq \mu + z_{\frac{\alpha}{2}} * (\frac{\sigma}{srt(n)}) - z_{\frac{\alpha}{2}} * (\frac{\sigma}{srt(n)}) &leq \overline{X_n} \\
\Rightarrow &\overline{X_n} = \mu
\end{align}
$$

This can be found by the mean of the two bounds of the interval itself, which is simply 4.7.

## Part B



# Problem 4

```{r}
x = iris$Sepal.Width[iris$Species == "virginica"]
```

## Part A

```{r}
alpha = 0.05
z_alpha_2 = qnorm(1 - alpha / 2)
sigma = 1 # because I don't know what else to use
l_n = mean(x) - z_alpha_2 * (sigma / length(x))
u_n = mean(x) + z_alpha_2 * (sigma / length(x))

cat(paste("Lower bound: ", l_n, "\nUpper bound: ", u_n))
```

## Part B

```{r}
alpha = 0.05
z_alpha_2 = qnorm(1 - alpha / 2)
sigma = sqrt(var(x))
l_n = mean(x) - z_alpha_2 * (sigma / length(x))
u_n = mean(x) + z_alpha_2 * (sigma / length(x))

cat(paste("Lower bound: ", l_n, "\nUpper bound: ", u_n))
```

## Part C

```{r}
y = x[1:10]

alpha = 0.05
z_alpha_2 = qnorm(1 - alpha / 2)

sigma = 1 # because I don't know what else to use
l_n = mean(x) - z_alpha_2 * (sigma / length(x))
u_n = mean(x) + z_alpha_2 * (sigma / length(x))

cat(paste("Lower bound: ", l_n, "\nUpper bound: ", u_n))

sigma = sqrt(var(y))
l_n = mean(x) - z_alpha_2 * (sigma / length(x))
u_n = mean(x) + z_alpha_2 * (sigma / length(x))

cat(paste("Lower bound: ", l_n, "\nUpper bound: ", u_n))
```

## Part D

The Gaussian confidence interval when unchanged, while the student one was modified only slightly. This is due
to the use of the experimental variance given the data, as the Student distribution relies on that instead of
a provided standard distribution.
